%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Intermediate Software Developer} % Job title
    {Smile CDR} % Organization
    {Toronto, Ontario} % Location
    {Jun. 2019 - present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Everything that matters.}
        \item {Designed and provisioned the entire infrastructure on the AWS cloud to meet security compliance and acquire a business license for financial services in Korea.}
        \item {Continuously improved the infrastructure architecture since launching the service. (currently 3.6 million users)}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Site Reliability Engineer} % Job title
    {Danggeun Market Inc.} % Organization
    {Seoul, S.Korea} % Location
    {Feb. 2021 - Mar. 2021} % Date(s)
    {
    }

%---------------------------------------------------------
  \cventry
    {Founding Member \& Director of Infrastructure Division} % Job title
    {Kasa} % Organization
    {Seoul, S.Korea} % Location
    {Jun. 2018 - Jan. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed on-boarding process to guide new engineers, help them to focus on the right tasks, and set expectations to help them be successful at Infrastructure team.}
        \item {Migrated the orchestration system from DC/OS to Kubernetes which is based on AWS EKS. Managed 3 Kubernetes clusters and 300+ pods. Managed all Kubernetes manifests declaratively with Kustomize and ArgoCD.}
        \item {Designed and managed complex network configurations on AWS with 4 VPC and 100+ subnets. Separated the development network and operation network according to financial regulations. Established dedicated network connections from AWS VPC to partners' on-premise network based on AWS Direct Connect with secure connection using IPsec VPN. Provisioned OpenVPN servers with LDAP integration.}
        \item {Provisioned a observability system with Kafka, Elastic Stack(Filebeat, Heartbeat, APM Server, Logstash, Elasticsearch, Kibana). Collected log, uptime, tracing data from hosts, containers, pods and more. The ES cluster which has 9 nodes processed more than 1 billion documents per month. Wrote Terraform module to easily provision ES cluster on AWS EC2 instances.}
        \item {Provisioned a monitoring system with Kafka, Telegraf, InfluxDB, Grafana. Collected metrics from hosts, containers, pods and more. Wrote Terraform module to easily provision InfluxDB with HA on AWS EC2 instances.}
        \item {Introduced Kong API Gateway to easily connect all API microservices with a declarative management method based on Terraform and Atlantis to collaborate and audit change history.}
        \item {Provisioned the Directory Service for employee identity management based on OpenLDAP which guarantees HA with multi-master replication.}
        \item {Implemented Worker microservices consuming Kafka event topics for email, SMS, Kakaotalk and Slack notification. Developed in-house framework to easily build Kafka consumer microservice with common features including retry on failure, DLQ(Dead Letter Queue), event routing and more.}
        \item {Introduced Elastic APM to help distributed tracing, trouble-shooting and performance testing in MSA.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed production ready, mobile friendly, AODA compliant web applications utilizing Angular 2+, OAuth standards, SCSS, and HTML5.}
        \item {Solidified knowledge of the FHIR standard, capable of developing user friendly front-end applications utilizing FHIR compliant API.}
        \item {Developed new features, fixed issues, configured and deployed various databases such as MSSQL, MySQL, MongoDB, and PostgreSQL.}
        \item {Worked with docker for deployments and for containerization of test environments.}
        \item {Strong knowledge of agile and scrum methodology, worked in sprint cycles with ticket tracking systems like Jira and GitLab.}
        \item {Worked with continuous integration technology such as gitlab CI/CD and Azure DevOps, to automate deployments.}
        \item {Strong knowledge of Angular 2+, developed an Angular library that's used in some client projects that's in production.}
        \item {Experience with Spring integration with Java, adding features and fixing issues that utilize Spring Context, Spring batch, Spring JPA, etc.}
        \item {Strong Java knowledge, worked in the core development team with a large code base, adding new important features and fixing issues.}
      \end{cvitems}
    }
  
%---------------------------------------------------------
    {Full-Stack Developer (Co-op)} % Job title
    {Ministry of Health and Long-Term Care} % Organization
    {Toronto, Ontario} % Location
    {Sep. 2017 - Aug. 2018} % Date(s)
        \item {Developed fully featured front-end applications and progressive web apps utilizing Angular 2+ and FHIR compliant API.}
        \item {Built and deployed back-end server infrastructure to Linux based OS such as red hat, utilizing Docker, Nginx, and IBM Cloud.}
        \item {Developed end-to-end applications using the Electron framework.}
        \item {Experience with Graphql query language, able to integrate with FHIR standard and full stack web application.}
        \item {Experience with NLP software such as dialog flow}
\end{cventries}
